Bringing the Power of eBPF to Open vSwitch

### 2018-11-01 paper.tex
minor fix
Import LPC.cls
If missing iftex.sty,
  $ apt-get install texlive-generic-extra
Update to LPC template
Header in the even page mess up. Not sure how to fix it.

\documentclass[10pt,numbers,reprint]{sigplanconf}

@@

\begin{document}
\title{Bringing the Power of eBPF to Open vSwitch}
\authorinfo{
  \(
  \begin{matrix}
    % Alphabetical order.
    \textrm{William Tu$^1$} & \textrm{Joe Stringer$^2$} & \textrm{Yifeng Sun$^1$} & \textrm{Yi-Hung Wei$^1$}\\
    \textrm{u9012063@gmail.com} & \textrm{joe@cilium.io} & \textrm{pkusunyifeng@gmail.com} & \textrm{yihung.wei@gmail.com} \\
  \end{matrix}
  \)
}
{
  \(
  \begin{matrix}
    \textrm{$^1$VMware Inc.} & \textrm{$^2$Cilium.io}\\
  \end{matrix}
  \)
}{}

@@

\section{Conclusion}
\label{sec:conclusion}
This paper describes two eBPF projects related to OVS: OVS-eBPF and OVS-AFXDP.

The eBPF project originally had the ambitious goal of replacing the fixed
kernel datapath with a dynamic datapath that may be injected on demand, while
keeping the design and operation essentially the same. This would solve
distribution and maintenance issues, as the version of the datapath would be
distributed with the OVS userspace package; furthermore, it would outline a
path to allow OVS to continue to process packets in the kernel without the use
of an OVS-specific kernel module, acheiving the goals of other recent
work~\cite{ovs_tc}. Collectively, this would allow the datapath logic to be
extended and modified more easily, while reducing the maintenance burden for
that code. Longer term, with a more flexible code base, many performance and
feature improvements could be made and more easily, as the constraints around
backwards compatibility of the fixed kernel ABI could be relaxed.

>>>>

\documentclass[10pt,numbers,reprint,sigconf,authorversion]{lpc}

@@

\begin{document}
\pdfinfo{
/Title (Bringing the Power of eBPF to Open vSwitch)
/Author (William Tu, Joe Stringer, Yifeng Sun and Yi-Hung Wei)}

\title{Bringing the Power of eBPF to Open vSwitch}
\author{William Tu}
\affiliation{%
      \institution{VMware Inc.}}
\email{u9012063@gmail.com}

\author{Joe Stringer}
\affiliation{%
      \institution{Cilium.io}}
\email{joe@cilium.io}

\author{Yifeng Sun}
\affiliation{%
      \institution{VMware Inc.}}
\email{pkusunyifeng@gmail.com}

\author{Yi-Hung Wei}
\affiliation{%
      \institution{VMware Inc.}}
\email{yihung.wei@gmail.com}

\acmDOI{}
\setcounter{secnumdepth}{0}
\setcopyright{none}

@@

\section{Conclusion}
\label{sec:conclusion}
This paper describes two eBPF projects related to OVS: OVS-eBPF and OVS-AFXDP.
The eBPF project originally had the ambitious goal of replacing the fixed
kernel datapath with a dynamic datapath that may be injected on demand, while
keeping the design and operation essentially the same. This would solve
distribution and maintenance issues, as the version of the datapath would be
distributed with the OVS userspace package; furthermore, it would outline a
path to allow OVS to continue to process packets in the kernel without the use
of an OVS-specific kernel module, acheiving the goals of other recent
work~\cite{ovs_tc}. Collectively, this would allow the datapath logic to be
extended and modified more easily, while reducing the maintenance burden for
that code. Longer term, with a more flexible code base, many performance and
feature improvements could be made and more easily, as the constraints around
backwards compatibility of the fixed kernel ABI could be relaxed.
